---
title: "Reproducible Research: Peer Assessment 1"
output:
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
##### 1. Load the data (i.e. read.csv())
```{r loaddata, results='markup', warning=TRUE, message=TRUE, echo=TRUE}
if(!file.exists('activity.csv')){
    unzip('activity.zip')
}
activityData <- read.csv('activity.csv')
```
##### 2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r processData, echo=TRUE}
activityData$interval <- strptime(gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", activityData$interval), format='%H:%M')
```
## What is mean total number of steps taken per day?
```{r stepsByDay, echo=TRUE}
stepsByDay <- tapply(activityData$steps, activityData$date, sum, na.rm=TRUE)
```

##### 1. Make a histogram of the total number of steps taken each day
```{r plotStepsByDay, echo=TRUE}
library("ggplot2")
qplot(stepsByDay, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```

##### 2. Calculate and report the mean and median total number of steps taken per day
```{r stepsByDayMean, echo=TRUE}
stepsByDayMean <- mean(stepsByDay)
stepsByDayMedian <- median(stepsByDay)
```
* Mean: `r stepsByDayMean`
* Median:  `r stepsByDayMedian`

-----

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
